\section{Our concrete result for TreeKEM}

The following theorem describing the security of TreeKEM, stated informally here, is our main practical result. It bounds the advantage of any adversary creating (at most) $c$ commits and $p$ add or update proposals in a group with at most $u$ users in distinguishing the group key of any uncompromised commit from a random bit string.

\begin{theorem}[Informal] \label{theorem:treekem-security-informal}
	If the DHIES scheme is used in TreeKEM, the private-key encryption scheme in DHIES is $(t, \eeav)$-EAV-secure and the DDH problem is $(t, \eddh)$-hard in the Diffie-Hellman group, then for all $c, p, u$, TreeKEM is $(\tilde{t}, \tilde{\epsilon}, c, p, u)$-secure in the ROM with $\tilde{t} \approx t$ and
	\begin{align*}
		\begin{split}
			\tilde{\epsilon} ={} & 2 \cdot u \cdot (3 \cdot c \cdot \log(u) + p) \cdot \eeav \\
			& + 2 \cdot (3 \cdot c \cdot \log(u) + p) \cdot \eddh \\
			& + \mathrm{negl}(\eta)
		\end{split}
	\end{align*}
	where
	\begin{itemize}
		\item $c$ is the number of commits created
		\item $p$ is the number of add or update proposals created
		\item $u$ is the maximum number of users
	\end{itemize}
\end{theorem}

In Section~\ref{sec:treekem-security} of the appendix we restate the above theorem formally as Theorem~\ref{theorem:treekem-security}. To this end, we also provide formal definitions for the syntax and security of propose and commit CGKA schemes and a high-level description of how to instantiate (the essence of) the TreeKEM protocol with our definitions.

\subsection{Interpreting the result}

In the following, we will go through some concrete examples to see what level of security our proof guarantees for TreeKEM with different parameter choices. We will look at the \texttt{MLS\_128\_DHKEMX25519\_AES128GCM\_SHA256\_Ed25519} cipher suite \cite[Section~17.1]{rfc9420} for 128-bit parameters, which uses Curve25519 as the Diffie-Hellman group and AES with a 128-bit key size for private-key encryption. We will assume that both Curve25519 and AES have a 128-bit security level and we will set $(t, \eeav) = (t, \eddh) = (2^{48}, 2^{-80})$.

For 256-bit parameters, we will look at the \texttt{MLS\_256\_DHKEMP521\_AES256GCM\_SHA512\_P521} cipher suite, which uses curve P-521 and 256-bit AES. We will assume that P-521 and 256-bit AES have a 256-bit security level and set $(t, \eeav) = (t, \eddh) = (2^{128}, 2^{-128})$.

\subsubsection{Large groups with hourly commits and frequent updates}

In this example we consider a large group of about 10'000 users, existing for 5 years and making one commit every hour. Then $u \le 2^{14}$ and $c \le 2^{16}$. We also assume that a significant fraction of the users will want to update with every commit. Then, assuming that add proposals are relatively rare, we can bound $p \le c \cdot u = 2^{30}$. This implies $3 \cdot c \cdot \log(u) + p \le 2^{31}$, dominated by $p$.

Then with 128-bit parameters we get
\[
	\et \le 2^{46} \cdot \eeav + 2^{32} \cdot \eddh + \mathrm{negl} \le \frac{1}{2^{33}}
\]
with the $\eeav$ term dominating the result. This only gives a security level of $\tilde{t}/\et \ge 2^{81}$. Since private-key encryption is relatively cheap, using 256-bit AES would have a small impact on the performance and would increase the security level to 95 bits (with the $\eddh$ term now dominating). Finally, using full 256-bit parameters yields 209 bits of security for TreeKEM.

The previous best result in \cite[Theorem 3]{ttkem} proved the bound
\[
	\et \le 2 \cdot (3 \cdot c \cdot \log(u) + p)^2 \cdot \epsilon + \mathrm{negl}
\]
where $\epsilon$ is the IND-CPA security of the underlying public-key encryption scheme. If we assume that DHIES has an $x$-bit security level as a public-key encryption scheme with $x$-bit parameters, the result implies 64 bits of security with 128-bit parameters (with no change when using 256-bit AES) and 192 bits with 256-bit parameters.

\subsubsection{Few updates}

In this example we use the same number of users and commits, but assume that the number of proposals is small such that $p \le c \cdot \log(u)$. In this case, we have $3 \cdot c \cdot \log(u) + p \le 2^{22}$. Then our result guarantees 90 bits of security with 128-bit parameters, 104 bits with 256-bit AES and 218 bits with 256-bit parameters.

In contrast, the bound in \cite{ttkem} implies 82 bits with 128-bit parameters and 210 bits with 256-bit parameters.

\subsubsection{Very large groups with one commit every minute and frequent updates} In this example we consider more extreme values for $c$ and $u$ to highlight the gap between our result and the one in \cite{ttkem}. We assume a group of about 1 million users, existing for 50 years and making one commit every minute. Furthermore, will again use $p \le c \cdot u$. This means that $u \le 2^{20}$, $c \le 2^{25}$ and $3 \cdot c \cdot \log(u) + p \le 2^{46}$.

These values imply a 61 bits of security with 128-bit parameters, 81 bits with 256-bit AES and 189 bits with 256-bit parameters using our result. The result in \cite{ttkem} implies 34 bits of security with 128-bit parameters and 162 bits with 256-bit parameters.
